---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

```{r}

library(tidyverse)
library(kernlab)
library(dbscan)
library(clValid)
library(factoextra)
library(uwot)
library(patchwork)
library(dplyr)
library(tidytext)
#library(stringer)
library(rscopus)
library(pdftools)
library(tm)
library(quanteda)
library(textstem)
library(gutenbergr)
library(wordcloud)
library(lsa)
library(stm)
library(text2vec)
library(rPref)
library(DT)
library(textdata)
library(knitr)
library(ggrepel)
library(caret)
set.seed(888)
rm(list = ls())
options(ggrepel.max.overlaps = Inf)

```

# Data reading and initial cleaning
```{r}

dat <- read.csv("~/ISYE 602/testthree.csv")
colnames(dat) = make.names(colnames(dat), unique = TRUE)

dat$Keywords[dat$Keywords == ""] <- NA

newdat <- na.omit(dat)

text_df <- tibble(line = 1:1694, text = newdat$Keywords)

text_df %>%
 unnest_tokens(word,text)

original <- newdat %>%
  group_by(Professor) %>%
  mutate(linenumber = row_number()) %>%
  ungroup()

tidyoriginal <- original %>%
  unnest_tokens(word, Keywords) ## Tidyoriginal contains professor names in one column with their respective keywords as individual rows in another column. The 'line number' column represents which research paper those keywords were from for that professor. 

```

# Further cleaning on text data
The following plot reveals each professor's name with the number of keywords included in the data from their publications. 
```{r tokenize_text}

## Numbers
tidyoriginal$word = gsub('[0-9]+', '', tidyoriginal$word)

## Periods
tidyoriginal$word = gsub('[.]+', '', tidyoriginal$word)

## Non-words
tidyoriginal$word = gsub('doi', '', tidyoriginal$word)
tidyoriginal$word = gsub('fig', '', tidyoriginal$word)

## Tokenize
researchtext.df = tidyoriginal %>% 
unnest_tokens(term, word, token = "words", 
                to_lower = TRUE, 
                strip_punct = TRUE) 

## One or two letters
researchtext.df = researchtext.df %>% filter(str_length(term)>2)

## Too many letters
researchtext.df = researchtext.df %>% filter(str_length(term)<15)

researchtext.df = researchtext.df %>% 
  anti_join(get_stopwords(), by = c("term" = "word"))

## Lemmatize
researchtext.df$term = lemmatize_words(researchtext.df$term)

researchtext.df %>% count(Professor) %>% 
ggplot(aes(n, reorder(Professor, -n))) +
  geom_col()+
 labs(x = "Total words in keywords", y = "")

```

Created additional data frame with all words grouped by professor for later use.
```{r}

groupedwords <- tidyoriginal %>%
  select(Professor, word) %>%
  group_by(Professor) %>%
  mutate(allwords = paste(word, collapse = " , "))

groupedwords <- tidyoriginal %>%
  group_by(Professor) %>%
  summarize(allwords = paste(word, collapse = " , "))

```


# Initial visualization of words via TF and IDF values
Word cloud, top words for each professor, and top words overall
```{r tf_idf, fig.height=4.5, warning=FALSE}

## Term frequency and tf_idf variables
researchtfidf.text.df = researchtext.df %>% count(Professor, term) %>% 
  bind_tf_idf(term, Professor, n)

## Infrequent words
researchtfidf.text.df = researchtfidf.text.df %>% filter(n>8)

## Indiscriminate words
researchtfidf.text.df = researchtfidf.text.df %>% filter(tf_idf>.000001)

## Wordcloud
wordcloud(researchtfidf.text.df$term, researchtfidf.text.df$n, min.freq = 5)

## Most discriminating terms
researchtop10.df = researchtfidf.text.df %>% group_by(Professor) %>% top_n(10, tf_idf) %>% 
  ungroup() %>% 
  mutate(Professor = as.factor(Professor))

ggplot(researchtop10.df, aes(reorder_within(term, tf_idf, within = Professor), tf_idf)) +
  geom_col() +
  coord_flip() +
  facet_wrap(.~Professor, scales = "free")+
  scale_x_reordered() 

## Scatterplot
ggplot(researchtop10.df, aes(idf, tf, size = tf_idf)) +
  geom_point(shape = 21, size = .75) +
  geom_text_repel(aes(label = term, size = tf_idf)) +
  facet_wrap(.~Professor) +
  theme_bw() +
  theme(legend.position = "none")

## Top tf_idf plot
ggplot(researchtop10.df, aes(idf, tf, size = tf_idf)) +
  geom_point(shape = 21, size = 1) +
  geom_text_repel(aes(label = term, size = tf_idf)) +
  theme_bw() +
  coord_trans(y="log") +
  theme(legend.position = "none")

rm(researchtop10.df)

``` 

# Latent semantic analysis
```{r lsa}

# Convert
researchtdm_weighted.tdmat = cast_tdm(researchtfidf.text.df, term, Professor, tf_idf)
researchtdm_count.tdmat = cast_tdm(researchtfidf.text.df, term, Professor, n)


## LSA
researchlsa_model <- lsa(researchtdm_count.tdmat,  dims=dimcalc_share(share = 0.75)) 

## Dimensions
dim(researchlsa_model$tk)
dim(researchlsa_model$dk)
length(researchlsa_model$sk)

## Expected value
as.textmatrix(researchlsa_model)

researchlsa_model <- lsa(researchtdm_weighted.tdmat,  dims=dimcalc_share(share = 0.75)) 

rm(researchtdm_count.tdmat)

```

# Dendrograms
The dendrogram of professors put most of the human factors researchers into the same cluster - pretty cool! 
```{r lsa_clustering, fig.height=6}

research.similiarity.mat = cosine(t(researchlsa_model$dk))

researchtemp = researchtfidf.text.df %>% 
  group_by(term) %>% 
  summarise(m.tf_idf = mean(tf_idf)) %>% 
  cbind(researchlsa_model$tk) %>% top_n(70, m.tf_idf) 

row.names(researchtemp)= researchtemp$term
researchterm.similiarity.mat = cosine(t(researchtemp %>% select(-term, -m.tf_idf))) 

research.dissimilarity.dist = as.dist(1-research.similiarity.mat)
researchterm.dissimilarity.dist = as.dist(1-researchterm.similiarity.mat)

researchdoc.cluster = hclust(research.dissimilarity.dist, method = "ward.D2", members = NULL)
plot(researchdoc.cluster)

researchterm.cluster = hclust(researchterm.dissimilarity.dist, method = "ward.D2", members = NULL)
plot(researchterm.cluster)

rm(researchtemp)

```

# UMAP Clusters
```{r}

researchterm.umap = umap(researchlsa_model$tk, n_neighbors = 20, n_components = 2) %>% 
  as.tibble()

names(researchterm.umap) = c("umap_1", "umap_2")

researchterm.umap = researchtfidf.text.df %>% group_by(term) %>% 
  summarise(m.tf_idf = max(tf_idf)) %>%
  cbind(researchterm.umap) 

researchterm.umap.plot = 
  ggplot(researchterm.umap, aes(umap_1, umap_2)) +
  geom_point(aes(size=m.tf_idf),shape = 21) +
  geom_label_repel(data = researchterm.umap %>% top_n(175, m.tf_idf),
                   aes(label = term), alpha = .6, size = 3) +
  labs(title = "UMAP clustering", subtitle = "20 nearest neighbors") +
  theme_void()+
  theme(legend.position = "none")
researchterm.umap.plot

researchdoc.umap = 
  umap(researchlsa_model$dk, n_neighbors = 3, n_components = 2) %>% 
  as.tibble()
names(researchdoc.umap) = c("umap_1", "umap_2")
researchdoc.umap = cbind(groupedwords, researchdoc.umap) # next is to compare this with other text analysis exercise

researchdoc.umap.plot = 
  ggplot(researchdoc.umap, aes(umap_1, umap_2)) +
  geom_point(aes(colour = Professor), size = 2.5) +
  geom_label_repel(aes(label = Professor), alpha = .6, size = 3) +
  labs(title = "UMAP clustering", subtitle = "3 nearest neighbors") +
  theme(legend.position = "none")
researchdoc.umap.plot

rm(researchterm.umap, researchterm.cluster, researchdoc.umap.plot, researchdoc.umap)

```

# Topic model analysis
```{r identify_topics, message=FALSE}

researchtext.sparse = researchtfidf.text.df %>% cast_sparse(Professor, term, n)

researchmulti_stm.fit = searchK(researchtext.sparse, 
                      K= c(3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13), 
                      M = 12,
                      init.type = "Spectral",
                      N = 4,
                      proportion = 0.5, 
                      heldout.seed = 888)

plot(researchmulti_stm.fit)

# Mimno, D., Wallach, H. M., Talley, E., & Leenders, M. (2011). Optimizing Semantic Coherence in Topic Models, (2), 262–272.

researchmultifit.results = researchmulti_stm.fit$results %>% unnest()

researchsky <- psel(researchmultifit.results, high(semcoh) * high(exclus))
researchCoherenceExclusivity.plot = ggplot(researchmultifit.results, aes(semcoh, exclus))+
  geom_point()+
  geom_text_repel(aes(label = K)) +
  geom_step(data = researchsky, direction = "hv") +
  labs(y = "Exclusivity", x = "Coherence")
researchCoherenceExclusivity.plot

researchsky <- psel(researchmultifit.results, high(heldout) * high(bound))
researchLikelihoodBound.plot = ggplot(researchmultifit.results, aes(heldout, bound))+
  geom_point() +
  geom_text_repel(aes(label = K)) +
  geom_step(data = researchsky, direction = "hv") +
  labs(y = "Heldout likelihood", x = "Lower bound of marginal likelihood")
researchLikelihoodBound.plot

rm(researchLikelihoodBound.plot, researchmultifit.results, researchCoherenceExclusivity.plot, researchsky)

```

# Proportions and FREX values
Not sure why this one is not letting group by professors.
```{r final_topicmodel, fig.height=4.5, message=FALSE}

researchtext.sparse = researchtfidf.text.df %>% cast_sparse(Professor, term, n)

researchtopic_model = stm(researchtext.sparse, K = 9, 
                   control = list(eta = .01, alpha = 50/8), 
                  verbose = FALSE, init.type = "Spectral")

researchtd_beta = tidy(researchtopic_model) 

researchtd_beta =
   researchtd_beta %>%
    group_by(topic) %>%
    top_n(10, beta) %>%
    ungroup()

researchfrex = labelTopics(researchtopic_model, n = 4)$frex %>% as.tibble() %>% unite(col = topic_name) 
researchfrex = cbind(topic = labelTopics(researchtopic_model, n = 3)$topicnums, researchfrex)
researchfrex$topic_number_name = paste(researchfrex$topic, researchfrex$topic_name, sep = "-") 
researchtd_beta = left_join(researchtd_beta, researchfrex)

researchtd_beta_ordered = researchtd_beta %>% 
  mutate(term_ordered = reorder_within(term , beta, topic))

ggplot(researchtd_beta_ordered, aes(term_ordered, beta)) +
  geom_col() +
  coord_flip() +
  facet_wrap(.~topic_number_name, scales = "free")+
  labs(title = "Prevalence of terms across topics", 
         x = "term", y = "Term prevalence (beta)") +
  scale_x_reordered() 

researchtd_gamma =
    tidy(researchtopic_model, matrix = "gamma",
         professor_names = rownames(researchtext.sparse))

researchtd_gamma = 
    researchtd_gamma %>% group_by(document) %>%
    mutate(dominant_topic = which.max(gamma))

researchtopic_names = researchtd_beta %>% select(topic, topic_number_name) %>% distinct()
researchtd_gamma = left_join(researchtd_gamma, researchtopic_names , by = "topic")
  
ggplot(researchtd_gamma, aes(as.factor(topic), gamma, fill = as.factor(topic_number_name))) +
    geom_col(width = .8, position = position_dodge(width = .2, preserve = "single")) +
    facet_grid(reorder(interaction(dominant_topic, document), dominant_topic)~.,
               scales = "free_x", drop = TRUE) +
    labs(title = "Prevalence of topics across professors", subtitle = "Most professors have one topic",
         x = "Topic", y = "Topic prevalence (gamma)") +
    theme(legend.position = "bottom", 
            axis.text.y = element_blank(),
            axis.ticks = element_blank(),
             strip.text.y = element_text(angle =0, hjust = 0))

# rm(researchtd_beta, researchtd_gamma, researchfrex, researchtopic_names)

```

# Sentiment analysis
```{r sentiment_terms}

get_sentiments("afinn") %>% datatable()
get_sentiments("bing") %>% datatable()
get_sentiments("nrc")[1:1000, ] %>% datatable()

```

```{r paper_sentiment}

researchsentiment.df = researchtext.df %>% group_by(Professor) %>% 
  mutate(total_terms = n()) %>% ungroup() %>% 
  inner_join(get_sentiments("bing"), by=c("term" = "word")) %>%
  group_by(Professor, sentiment) %>% 
  summarise(n = n(), total_terms= first(total_terms)) %>% 
  ungroup() %>% group_by(Professor) %>% 
  mutate(proportion = n/total_terms) %>% group_by(Professor, sentiment) %>% 
  mutate(signed.proportion = replace(proportion, sentiment=="negative", -proportion)) %>% 
  ungroup() %>% 
  group_by(Professor) %>% 
  mutate(sum_sentiment = sum(signed.proportion))

ggplot(researchsentiment.df, 
       aes(reorder(Professor, sum_sentiment), signed.proportion, fill = sentiment))+
  geom_col() +
  coord_flip() +
  labs(x = "Professors ordered by net proportion of positive sentiment", 
       y = "Proportion of positive and negative words") +
  theme(legend.position = "none")

```

```{r sentiment_influencers}

researchinfluence_sentiment.df = researchtext.df %>% 
  inner_join(get_sentiments("bing"), by=c("term" = "word")) %>% 
  count(Professor, sentiment, term) %>% 
  group_by(Professor, sentiment) %>% 
  top_n(n, n = 5) %>% slice(1:5) %>% # Limits to 5 in case of ties
  mutate(signed.sentiment = replace(n, sentiment=="negative", -n))  
  
ggplot(researchinfluence_sentiment.df, aes(reorder_within(term, n, Professor), signed.sentiment, fill = sentiment)) +
  geom_col() +
  coord_flip() +
  facet_wrap(.~Professor, scales = "free")+
  scale_x_reordered() +
  labs(x= "Words that strongly contribute to professor sentiment", y = "Positive and negative sentiment") +
  theme(legend.position = "none")

```

```{r}

researchsentiment.df.afinn = researchtext.df %>% group_by(Professor) %>% 
  mutate(total_terms = n()) %>% ungroup() %>% 
  inner_join(get_sentiments("afinn"), by=c("term" = "word")) %>% 
rename(sentiment = value) %>%
  group_by(Professor, sentiment) %>% 
  summarise(n = n(), total_terms= first(total_terms)) %>%
  ungroup() %>% group_by(Professor) %>%
  mutate(proportion = n/total_terms) %>% group_by(Professor, sentiment) %>%
  mutate(signed.proportion = replace(proportion, sentiment <0, -proportion)) %>%
  ungroup() %>%
  group_by(Professor) %>%
  mutate(sum_sentiment = sum(signed.proportion))

ggplot(researchsentiment.df.afinn, 
       aes(reorder(Professor, sum_sentiment), signed.proportion, fill = sentiment))+
  geom_col() +
  coord_flip() +
  labs(x = "Professors ordered by net proportion of positive sentiment", 
       y = "Proportion of positive and negative words") +
  theme(legend.position = "none")

```

# Glove embedding
```{r}
## Embeddings downloaded from: https://nlp.stanford.edu/projects/glove/

glove = read_delim(file = "/Users/madel/Documents/ISYE 602/ExFive/glove.6B.100d.txt", 
                   progress =FALSE,
                   col_names = FALSE, delim = " ", quote = "")
names(glove)[1] = "token"

```


```{r, message=FALSE, fig.height=6}

researchglovec.text.df = researchtext.df %>% 
  inner_join(glove, by=c("term" = "token"))

researchs.glovec.text.df = researchglovec.text.df %>% 
  gather(key = glovec_id, value = glovalue, contains("X")) %>% 
  group_by(Professor, glovec_id) %>% 
  summarise(m.glovalue = mean(glovalue)) %>% 
  spread(key = glovec_id, value = m.glovalue) %>% 
  ungroup()

researchdoc.similiarity.mat = cosine(t(researchs.glovec.text.df %>% select(contains("X")) %>% as.matrix()))  
row.names(research.similiarity.mat) = as.vector(researchs.glovec.text.df$Professor)
  
research.dissimilarity.dist = as.dist(1-research.similiarity.mat)

researchdoc.cluster = hclust(research.dissimilarity.dist, method = "ward.D2", members = NULL)
plot(researchdoc.cluster)

```

```{r}

 research.umap = researchs.glovec.text.df %>% select(starts_with("X")) %>% 
   umap(n_neighbors = 3, n_components = 2) %>% 
   as.tibble()
 names(research.umap) = c("umap_1", "umap_2")
 research.umap = cbind(groupedwords, research.umap)

research.umap.plot = 
  ggplot(research.umap, aes(umap_1, umap_2)) +
  geom_point(aes(colour = Professor), size = 2.5) +
  geom_label_repel(aes(label = Professor), alpha = .6, size = 3) +
  labs(title = "UMAP clustering", subtitle = "3 nearest neighbors") +
  theme_void()+
  theme(legend.position = "none")
research.umap.plot

```

```{r}

researchterms.df = researchtfidf.text.df %>% group_by(term) %>% 
  summarise(m.tf_idf = max(tf_idf)) %>% 
  inner_join(glove, by=c("term" = "token"))

researchterm.umap = researchterms.df %>% select(starts_with("X")) %>% 
  umap(n_neighbors = 10, n_components = 2) %>% 
  as.tibble()
names(researchterm.umap) = c("umap_1", "umap_2")

researchterm.umap =  researchterms.df %>%
  cbind(researchterm.umap) 

researchterm.umap.plot = 
  ggplot(researchterm.umap, aes(umap_1, umap_2)) +
  geom_point(aes(size=m.tf_idf),shape = 21) +
  geom_label_repel(data = researchterm.umap %>% top_n(100, m.tf_idf),
                   aes(label = term), alpha = .6, size = 3) +
  labs(title = "UMAP clustering", subtitle = "20 nearest neighbors") +
  theme_void()+
  theme(legend.position = "none")
researchterm.umap.plot

```

# Canonical correlation
```{r, fig.height=4.5}

researchcombined.embedding = cbind(researchs.glovec.text.df, researchlsa_model$dk)

researchglovector = researchs.glovec.text.df %>% select(contains("X")) %>% as.matrix

researchcombined.embedding.kcca = kcca(researchlsa_model$dk, researchglovector,
     kernel="rbfdot", kpar=list(sigma=0.1),
     gamma = 0.1, ncomps = 30)

researchcombined.embedding.kcca.mat = cbind(researchcombined.embedding.kcca@xcoef, researchcombined.embedding.kcca@xcoef)

research.similiarity.mat = cosine(t(researchcombined.embedding.kcca.mat))  
row.names(research.similiarity.mat) = as.vector(researchs.glovec.text.df$Professor)
  
research.dissimilarity.dist = as.dist(1-research.similiarity.mat)

research.cluster = hclust(research.dissimilarity.dist, method = "ward.D2", members = NULL)
plot(research.cluster)

```







# Attempt at utilizing scopus package (ignore for now)
Having issues trying to set up API key - could try creating my own API through the website when logged in but not sure if that is needed
```{r}

#get_author_info(last_name = "Lee", first_name = "John",
 # affil_id = NULL, affil_name = "University of Wisconsin-Madison")


#omplete_author_info(last_name = NULL, first_name = NULL,
 # affil_id = NULL, affil_name = NULL, api_key = NULL,
#  http = "https://api.elsevier.com/content/search/author",
#  query = NULL, count = 200, start = 0, verbose = TRUE,
#  au_id = NULL, headers = NULL, ...)

```

